Rank Recovery

### 2020-11-09 output_scripts/rank_recovery.Rmd
modify to simulate data from dc mmhp model to see the results

---
title: "Rank Recovery"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

@@

@@

```{r recover cmmhp model, cache=TRUE}
# model3 <- stan_model(here("lib","sim_model3.stan"))
model3 <- cmdstan_model(here("lib","sim_model3.stan"))
data_list <- list(max_Nm=max(clean_sim_data$N_count),
                    N_til = length(clean_sim_data$I_fit),
                    M=sum(clean_sim_data$N_count>=cut_off),
                    N=length(object_par$f_vec_1),
                    I_fit = clean_sim_data$I_fit,
                    J_fit = clean_sim_data$J_fit,
                    T = tail(clean_sim_data$day_hour,1),
                    Nm = as.vector(clean_sim_data$N_count[clean_sim_data$N_count 
                                                          >= cut_off]),
                    event_matrix = clean_sim_data$event_matrix,
                    interevent_time_matrix = clean_sim_data$time_matrix,
                    max_interevent = clean_sim_data$max_interevent)

model3_stan_fit <- model3$sample(data = data_list,
                                iter_warmup = 500,
                                iter_sampling = 500,
                                chains = 4, 
                                parallel_chains = 4,
                                refresh = 100)

@@

```{r extract stan fit}
stanfit <- rstan::read_stan_csv(model3_stan_fit$output_files())

@@

```{r fit dc mmhp, cache=TRUE}
model3_dc <- cmdstan_model(here("lib","sim_model3_dc.stan"))
data_list_dc <- list(max_Nm = max(clean_sim_data_dc$N_count),
                    N_til = length(clean_sim_data_dc$I_fit),
                    M=sum(clean_sim_data_dc$N_count>=cut_off),
                    N=length(object_par$f_vec_1),
                    I_fit = clean_sim_data_dc$I_fit,
                    J_fit = clean_sim_data_dc$J_fit,
                    T = tail(clean_sim_data_dc$day_hour,1),
                    Nm = as.vector(clean_sim_data_dc$N_count[
                      clean_sim_data_dc$N_count 
                                                          >= cut_off]),
                    event_matrix = clean_sim_data_dc$event_matrix,
                    interevent_time_matrix = clean_sim_data_dc$time_matrix,
                    max_interevent = clean_sim_data_dc$max_interevent)

@@

stanfit_dc <- rstan::read_stan_csv(model3_dc_stan_fit$output_files())
stansims_dc <- rstan::extract(stanfit_dc)
## truth is .1, .2, .4, .7, .9
apply(stansims_dc$f, 2, mean)
apply(stansims_dc$f, 2, sd)

@@

So when we consider this degree corrected model we also
correctly recover the latent ranking order in this simulation.

>>>>

---
title: "Rank Recovery"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: TRUE
    code_folding: hide
---

@@

## Simulated data from original model

@@

```{r recover cmmhp model, eval=FALSE ,cache=TRUE}
# model3 <- stan_model(here("lib","sim_model3.stan"))
model3 <- cmdstan_model(here("lib","sim_model3.stan"))
data_list <- list(max_Nm=max(clean_sim_data$N_count),
                    N_til = length(clean_sim_data$I_fit),
                    M=sum(clean_sim_data$N_count>=cut_off),
                    N=length(object_par$f_vec_1),
                    I_fit = clean_sim_data$I_fit,
                    J_fit = clean_sim_data$J_fit,
                    T = tail(clean_sim_data$day_hour,1),
                    Nm = as.vector(clean_sim_data$N_count[clean_sim_data$N_count 
                                                          >= cut_off]),
                    event_matrix = clean_sim_data$event_matrix,
                    interevent_time_matrix = clean_sim_data$time_matrix,
                    max_interevent = clean_sim_data$max_interevent)

model3_stan_fit <- model3$sample(data = data_list,
                                seed = 123,
                                iter_warmup = 50,
                                iter_sampling = 50,
                                chains = 4, 
                                parallel_chains = 4,
                                refresh = 100)
model3_stan_fit$save_object(file = here("output", "rank_sims", 
                                        "rmd_stan",
                                        "model_3_stan_fit.RDS"))

@@

```{r extract stan fit}
model3_stan_fit <- readRDS(here("output", "rank_sims", 
                                        "rmd_stan",
                                        "model_3_stan_fit.RDS"))
stanfit <- rstan::read_stan_csv(model3_stan_fit$output_files())

@@

```{r fit dc mmhp, eval=FALSE}
model3_dc <- cmdstan_model(here("lib","sim_model3_dc.stan"))
data_list_dc <- list(max_Nm = max(clean_sim_data_dc$N_count),
                    N_til = length(clean_sim_data_dc$I_fit),
                    M=sum(clean_sim_data_dc$N_count>=cut_off),
                    N=length(object_par$f_vec_1),
                    I_fit = clean_sim_data_dc$I_fit,
                    J_fit = clean_sim_data_dc$J_fit,
                    T = tail(clean_sim_data_dc$day_hour,1),
                    Nm = as.vector(clean_sim_data_dc$N_count[
                      clean_sim_data_dc$N_count 
                                                          >= cut_off]),
                    event_matrix = clean_sim_data_dc$event_matrix,
                    interevent_time_matrix = clean_sim_data_dc$time_matrix,
                    max_interevent = clean_sim_data_dc$max_interevent)

@@

model3_dc_stan_fit$save_object(file = here("output", "rank_sims", 
                                        "rmd_stan",
                                        "model_3_dc_stan_fit.RDS"))
```

```{r load dc stan fit}
model3_dc_stan_fit <- readRDS(here("output", "rank_sims", 
                                        "rmd_stan",
                                        "model_3_dc_stan_fit.RDS"))
stanfit_dc <- rstan::read_stan_csv(model3_dc_stan_fit$output_files())
stansims_dc <- rstan::extract(stanfit_dc)
## truth is .1, .2, .4, .7, .9
apply(stansims_dc$f, 2, mean)
apply(stansims_dc$f, 2, sd)

@@

table(true_rank, m3_rank)
table(true_rank, isi_rank_dc)
table(isi_rank_dc, m3_rank)
```

So when we consider this degree corrected model we also
correctly recover the latent ranking order in this simulation from 
both the stan fit and the I&SI model.
